---
title: "BBC Rap Music Rankings"
author: "Ochiwar"
date: "4/16/2020"
output: 
    html_document:
        theme: cosmo
        highlight: monochrome
        toc: true
        toc_float: false
        toc_depth: 4
        code_folding: hide
---
<style>
body, h1, h2, h3, h4 {
    font-family:"Calibri", serif;
}

body {
    color: #333333;
}
a, a:hover {
    color: red;
}
pre {
    font-size: 10px;
}
</style>

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, cache = TRUE, 
                      warning = FALSE, message = FALSE, 
                      dpi = 100, fig.width = 8, fig.height = 5)
```


## Load Libraries

```{r}
library(tidyverse)
library(lubridate)
```


## Load Data

```{r}
tuesdata <- tidytuesdayR::tt_load("2020-04-14")

polls <- tuesdata$polls
rankings <- tuesdata$rankings

head(polls)
head(rankings)
```

## Data Wrangling

Most critics in the dataset are male. Only 7% of critics identify as female and 88% identify as male. Does rap music have a gender appeal or do we just have more males in the 'music critic' business? 

```{r, warning=FALSE, echo=FALSE}
gender_tbl <- polls %>% 
    count(gender, name = "count") %>%
    mutate(prop = scales::percent(count/sum(count))) %>% 
    arrange(desc(prop))

knitr::kable(gender_tbl)

```

## Data Analysis

#1
How many of these critics have their primary country listed as US? 

```{r}
polls %>% 
    count(critic_country) %>% 
    arrange(desc(n)) %>% 
    knitr::kable()
```



Which decade had the most mentions

```{r echo=FALSE}
library(extrafont)

decade_spread <- polls %>% 
    select(year) %>% 
    mutate(decade = year - year%%10 ) %>% 
    group_by(decade) %>% 
    count()  
    
decade_spread %>% 
    ggplot(aes(decade, n)) +
    geom_bar(stat = "identity", fill = "salmon") +
    geom_text(aes(label = n), hjust = 1.2, family = "Arial Narrow", size = 5)+
    coord_flip() + 
    labs(
        y = "",
        x = "",
        title = "Most Critics Selected and Ranked Songs from the 1990s"
    )+
    theme_minimal() +
    theme(
        text = element_text(family = "Calibri"),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 13, family = "Arial Narrow"),
        plot.title = element_text(size = 16), 
        plot.background = element_rect(color = "gray")
    )
   
```

How did the critics rank songs across the years choosen

```{r}
rankings %>% 
    ggplot(aes(year, points)) +
    geom_point(size = 2) + 
    geom_smooth(se = F) +
    scale_y_continuous(trans = "sqrt")
```




Critics Top Ranked Song Titles with their Artists

```{r}
library(glue)
top_six_tbl <- polls %>% 
    count(artist, title) %>% 
    arrange(desc(n)) %>% 
    filter(n >= 10) %>% 
    inner_join(rankings, by = c("artist", "title"), suffix = c("_poll", "_ranking")) %>% 

    select(artist, title, n_poll, points) %>% 
    mutate(artist = factor(artist) %>% fct_reorder(points, max))

#levels(top_six_tbl$artist)

top_six_tbl %>% 
    ggplot(aes(artist,points)) +
    geom_col() + 
    geom_text(aes(label = glue("title:{title}\npoints:{points}")), hjust = 1.1, fontface = "bold") +
    coord_flip() + 
    
    labs(
        y = "",
        x = "",
        title = "Critics Top Ranked Titles with their Artists"
    )+
    theme_minimal(16) +
    theme(
        text = element_text(family = "Calibri"),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 13, family = "Arial Narrow"),
        plot.title = element_text(size = 16, hjust = 0.1), 
        plot.background = element_rect(color = "gray")
    )
    
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
