---
title: "Coffee Study"
author: "Ochiwar"
date: "7/10/2020"
output: 
    pdf_document:
        toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo    = FALSE,
                      message = FALSE,
                      include = FALSE)
```

```{r libriaries}

library(tidyverse)
library(tidytuesdayR)
library(kableExtra)
library(patchwork)
library(extrafont)
```

# Load Weekly Data

```{r }

tt <- tt_load("2020-07-07")

coffee_ratings <- tt$coffee_ratings

```
\newpage

# Glimpse Data

```{r Glimpse, include=TRUE}

glimpse (coffee_ratings)

```
\newpage

## Personal Notes

\begin{itemize}
    \item How does the processing method affect overall evaluation
    \item Does the part of the country where coffee is grown affect evaluation 
    \item Does the difference in harvest year and grading date impact evaluation 
    \item Does altitude have an impact on evaluation. The higher you go the cooler it becomes
    \item Relationship between color of grain and country of bean/mill origin 
    \item total cup points...whats that? 
\end{itemize}


\newpage

# List of African Countries

```{r include = TRUE}

african_countries <- c(
  "Ethiopia",
  "Kenya",
  "Burundi",
  "Rwanda",
  "Malawi",
  "Zambia",
  "Mauritius",
  "Cote d'Ivoire",
  "Tanzania"
)


kable(african_countries, "latex", booktabs = T)

```


# Tidy and Get Average Scores 

```{r coffee_scores, include=TRUE, warning=FALSE }

coffee_scores <- coffee_ratings %>% 
    mutate(
        country_of_origin = case_when(
                                      country_of_origin == "Cote d?Ivoire" ~ "Cote d'Ivoire", 
                                      country_of_origin == "Tanzania, United Republic Of" ~ "Tanzania", 
                                      TRUE ~ country_of_origin                          
                                      )
    ) %>% 
    filter(country_of_origin %in% african_countries) %>% 
    select(country_of_origin, total_cup_points, 21:31 ) %>% 
    group_by(country_of_origin) %>% 
    summarise(across(is.numeric, mean)) %>% 
    ungroup() %>% 
    mutate(across(is.numeric, round, digits = 2)) %>% 
    arrange(desc(total_cup_points))
     

kable(coffee_scores, "latex", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"))

```
\newpage

# Avg Category Scores


```{r coffee_scores_long, include=TRUE}

coffee_scores_long <- coffee_scores %>% 
  pivot_longer(
    names_to  = "category",
    values_to = "score", 
    cols      = aroma:moisture
  ) %>%  
  
  mutate(
    category = str_to_title(category),
    category = str_replace(category, "_", " ")
  ) %>% 
  filter(!category %in% c("Moisture", "Cupper points")) %>% 
  group_by(country_of_origin) %>% 
  mutate(avg_score = mean(score))

kable(coffee_scores_long, "latex", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"))

```
\newpage

# Make Overall Score Plot


```{r}

p1 <- coffee_scores %>% 
  mutate(max = 100) %>% 

  ggplot(aes(reorder(country_of_origin, total_cup_points), total_cup_points)) +
  
  geom_segment(
    aes(x = reorder(country_of_origin, total_cup_points), 
        xend = country_of_origin, 
        y = 0, yend = 100),
    color = "grey70",
    lty = 2
    ) +
  
  geom_segment(
      aes(x = country_of_origin, xend = country_of_origin, y = 0, yend = total_cup_points),
      color = "grey50"
    ) +
  
  geom_point(shape = 21,
             fill = "#F0F0F0",
             color = "grey25") +
  
  geom_point(aes(country_of_origin, max),
             size = 2,
             color = "grey25") +
  
  labs(
    x = NULL,
    y = NULL,
    title = ""
  ) +
  
  geom_text(
    aes(label = round(total_cup_points)),
    size = 2.5,
    vjust = -1,
    family = "Arial Narrow"
  ) +
  
  scale_y_continuous(
    limits = c(0, 100), 
    position = "right", 
    breaks = c(0, 50, 100)
  ) +
  
#  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  coord_flip() +
  theme(
    rect = element_rect(fill = "#F2EBE4", color = NA),
    panel.background = element_rect(fill = "#F2EBE4"),
    strip.background = element_rect(fill = "#F2EBE4"),
    plot.margin = margin(0,0,0,0),
    panel.grid = element_blank(),
    axis.text.x = element_blank(),
    axis.title.x.top = element_blank()
  )


```


```{r}
# make category plot
p2 <-
  coffee_scores_long %>% 
  ungroup() %>% 
  mutate(country_of_origin = factor(country_of_origin),
         country_of_origin = forcats::fct_reorder(country_of_origin, -total_cup_points)) %>% 
  
  ggplot() +
  geom_hline(
    aes(yintercept = avg_score), 
    color = "grey50",
    size = 0.25,
    alpha = 0.75
    ) +
  
  geom_segment(
      aes(x = reorder(category, score), 
          xend = category, 
          y = 0, yend = 10),
      color = "grey70",
      lty = 2
    ) +
  
  geom_segment(
      aes(x = category, xend = category, y = 0, yend = score),
      color = "grey50"
    ) +
  
  geom_point(aes(category, 10),
             size = 2,
             color = "grey25") +
  
  geom_point(
    aes(reorder(category, score), score),
    shape = 21,
    fill = "#F0F0F0",
    color = "grey25"
    ) +
  
  labs(
    x = NULL,
    y = NULL,
    title = ""
  ) +
  
  scale_x_discrete(
    position = "bottom"
  ) +
  
  scale_y_continuous(
    limits = c(0, 10), 
    position = "right", 
    breaks = c(10)
    ) +
  
  coord_flip() +
  
  facet_wrap(country_of_origin~., ncol = 2) +
  
  theme(
    rect = element_rect(fill = "#F2EBE4", color = "black"),
    panel.background = element_rect(fill = "#F2EBE4", color = "#F2EBE4"),
    strip.background = element_rect(fill = "#F2EBE4"),
    panel.grid = element_blank(),
    #plot.margin = margin(-1,-1,0,0),
    axis.text.x = element_text(size = 6),
    # axis.title.x.top = element_blank(),
    axis.text.y = element_text(size = 6),
    strip.text = element_text(size = 8),
    strip.placement = "outside"
    )

```



```{r include = TRUE}
# patch together with {patchwork} & add labels

p1 + 
  p2 +
  plot_annotation(
    title = "African Originated Coffee Ratings",
    caption = "@MaiaPelletier | #TidyTuesday | James LeDoux (Coffee Quality Database)"
    ) &
  theme(
    rect = element_rect(fill = "#F2EBE4", color = "black"),
    text = element_text("Arial Narrow"),
    plot.title = element_text(hjust = 0.5, margin = margin(0, 0, -10, 0), size = 14),
    plot.caption.position = "panel",
    plot.caption = element_text(size = 5)
    ) -> p

p
```


```{r}

p+
 ggsave(paste0("imgs_week28_", format(Sys.time(), "%Y%m%d"), ".png"), type = 'cairo')

```

